Types From Data: \textnormal{Making structured schema-free data formats first-class citizens in F\#}

### 2015-11-17 pldi-2016/paper.tex
Update paper.tex

Any non-nullable type can be wrapped in the \kvd{option} constructor to explicitly permit the 
\kvd{null} value. Type providers map \kvd{option} to standard F\# option. A collection $[\sigma]$ 
is also nullable and missing values or \kvd{null} are treated as empty collections. The type 
$\kvd{null}$ is inhabited by the $\kvd{null}$ value (using an overloaded notation) and $\bot$ 
is the bottom type.

@@

Although all variants are mutual subtypes, we find one that best represents the sample. We avoid
nested variants and limit the number of cases. This is done by grouping types 
that have a common supertype which is not a variant. For example, rather than inferring 
$\kvd{any}\langl\ident{int}, \kvd{any}\langl\ident{bool}, \ident{decimal}\rangl\rangl$, 
our algorithm finds the common supertype of $\ident{int}$ and $\ident{decimal}$ and produces 
$\kvd{any}\langl\ident{decimal},\ident{bool}\rangl$. To identify types that have a common supertype 
which is not a variant, we group the types by a tag. The tag of a type is obtained using a function 
\tytagof{(-)}. The function is not defined on $\bot$ and $\kvd{null}$ as those are hanled by the 
(\emph{bot}) and (\emph{null-1}) or (\emph{null-2}).

>>>>

Any non-nullable type can be wrapped in the \kvd{option} constructor to explicitly permit the 
\kvd{null} value. Type providers map \kvd{option} to the standard F\# option type. A collection $[\sigma]$ 
is also nullable and missing values or \kvd{null} are treated as empty collections. The type 
$\kvd{null}$ is inhabited by the $\kvd{null}$ value (using an overloaded notation) and $\bot$ 
is the bottom type.

@@

Although all variants are mutual subtypes, we find one that best represents the sample. We avoid
nested variants and limit the number of cases. This is done by grouping types 
that have a common supertype which is not a variant. For example, rather than inferring 
$\kvd{any}\langl\ident{int}, \kvd{any}\langl\ident{bool}, \ident{decimal}\rangl\rangl$, 
our algorithm finds the common supertype of $\ident{int}$ and $\ident{decimal}$ and produces 
$\kvd{any}\langl\ident{decimal},\ident{bool}\rangl$. To identify types that have a common supertype 
which is not a variant, we group the types by a tag. The tag of a type is obtained using a function 
\tytagof{(-)}. The function is not defined on $\bot$ and $\kvd{null}$ as those are handled by the 
(\emph{bot}) and (\emph{null-1}) or (\emph{null-2}).
